### 2020-05-29 writeup/transfer.tex

	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, consider the following family of matrices
	\begin{align*}
		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{ M^\top M} \le \mu^p, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
	\end{align*}
	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$.
	Similar to the isotropic model, we assume that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1$ equals $\beta_2$ plus i.i.d. entries with mean $0$ and variance $d^2$.
	The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.

\begin{proposition}[Covariate shift]\label{prop_covariate}
	In the setting described above, assume that $\rho_1 > 3$ and $\rho_2>3$,
and $\|\Sigma_1\|\le C_1$ for some constant $C_1>0$.
	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1} + \frac{1}{\sqrt {\rho_1}}}} \min_{M\in\cS_{\mu}} g(M). \]
\end{proposition}
Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,

>>>>

	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, consider the following family of matrices
	\begin{align*}
		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{ M^\top M} \le \mu^p, \lambda(M) \in [\mu_{\min}, \mu_{\max}]},
	\end{align*}
	where $\mu, \mu_{\min}, \mu_{\max}$ are fixed values that do not grow with $p$. We first assume that there is no model bias. 
	Similar to the isotropic model, we assume that $\beta_1=\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$.
	The following proposition shows that when $n_1$ is much larger than $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized at $M = \mu\id$ among all matrices in $\cS_{\mu}$.

\begin{proposition}[Covariate shift]\label{prop_covariate}
	In the setting described above, assume that $\rho_1 > 1$ and $\rho_2>1$.
	Let $g(M)$ denote the test error of $\hat{\beta}_t^{\MTL}$ when the covariance shift matrix is equal to $M\in\cS_{\mu}$.
	We have that \[ g(\mu\id) \le \bigbrace{1+ \bigo{\frac{\rho_2}{\rho_1}  }} \min_{M\in\cS_{\mu}} g(M). \]
\end{proposition}
Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,
